---
title: "8d4f0b42"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of the impact of savings rate on GDP growth rate 

Description: This is a package to analyze the macroeconomics data for a country,basing on the data from Word Bank.  Users can input a symbol for a country to acquire the country's macroeconomics data(gdp,gdp growth rate and saving rate). For example, gdp('US').It also plots the growth rate of 'BRICKS' countries, which shows the five countris growth path.


##Function to acquire macroeconomics data of a country
```{r cars}
library(ggplot2)
library(WDI)
library(plotly)
#Macro data aquisition
gdp<-function(symbol){
  saving <- WDI::WDI(country=symbol,
                     indicator="NY.GNS.ICTR.ZS",
                     start=1990, end=2018)
  gdp <- WDI::WDI(country=symbol,
                  indicator="NY.GDP.MKTP.CD",
                  start=1990, end=2018)
  DF = WDI::WDI(country=symbol,
                indicator="NY.GDP.MKTP.KD.ZG",
                start=1990, end=2018)
  macro<-data.frame(
    Gdp=gdp,
    Savingrate=saving,
    Growthrate=DF
  )
  print(macro)
}
```

#Data Visualization
#GDP growth rate of "BRICKS" countries#
 
```{r pressure, echo=FALSE}
DF = WDI::WDI(country=c("CN","RU","BR","ZA","IN"),
              indicator="NY.GDP.MKTP.KD.ZG",
              start=1990, end=2018)

ggplot(DF, aes(year, NY.GDP.MKTP.KD.ZG, color=country))+
  geom_line()+geom_point()+xlab("Year")+
  labs(title = "Annual GDP Growth rate (%)")+ylab("")

#Analyze the relationship between gdp growth rate and saving rate
relation<-glm(macrodata[,11]~macrodata[,7])
summary(relation)

According to the regression analysis, the saving rate has a positive effect on the gdp growth rate. For example, concerning USA,every one percent increment of saving rate adds 0.5638% to GDP growth rate.


```

